Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-05-03 faces_system.tex
Fixed double Zihan typo, and updated Hossein's bio.

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/zihan}}]{Zihan Zhou}
Zihan Zhou received the bachelor's degree in automation from Tsinghua
University, China, in 2007. Since then, he has been with University of Illinois
at Urbana-Champaign, where he received the MS degree in electrical and computer
engineering and where he is now working toward the PhD degree. During the
summer of 2009, he was a research intern with Microsoft Research Asia, Beijing.
His research interests include computer vision, signal processing and machine
learning. 
\end{IEEEbiography}

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]
{bios/hossein}}]{Hossein Mobahi} received his Bachelor's and Master's degrees
in Iran, both in Computer Engineering from Azad University (Tehran-South) in
2003  and University of Tehran in 2005 respectively. He is currently a PhD
candidate in the Computer Science Department at the University of Illinois,
Urbana-Champaign. His research interests include pattern classification,
clustering and optimization.  His recent research focuses on iterative
smoothing for image alignment.  \end{IEEEbiography}

>>>>

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/zihan}}]{Zihan Zhou}
received the bachelor's degree in automation from Tsinghua
University, China, in 2007. Since then, he has been with University of Illinois
at Urbana-Champaign, where he received the MS degree in electrical and computer
engineering and where he is now working toward the PhD degree. During the
summer of 2009, he was a research intern with Microsoft Research Asia, Beijing.
His research interests include computer vision, signal processing and machine
learning. 
\end{IEEEbiography}

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]
{bios/hossein}}]{Hossein Mobahi} is currently a PhD
candidate in the Computer Science Department at the University of Illinois,
Urbana-Champaign. His research interests include pattern classification,
clustering and optimization.  His recent research focuses on iterative
smoothing for image alignment.  \end{IEEEbiography}
